Cats and Dogs Recognition

### 2013-12-06 paper.tex
th

\section {Combination of Color and Texture Feature}
We need to come up with a way to combine color and texture features to get a better classifier. Assume that color feature vector has a length of $N_c$, the texture feature has a length of $N_t$. Our first approach is to concatenate the two feature vectors into a longer feature vector with a length of $N_c + N_t$. Then we will run boosting algorithm using the new feature vector. \\
The second approach is combining two classifiers instead of combing two feature vectors. Recall that for boosting classifier, each picture will have a voting. Assume that classfier 1 gives the picture a voting $v_1$, and classifier 2 gives the picture a voting $v_2$. Given parameter $\alpha$, we calculate a new voting $ v = \alpha \times v_1 + (1-\alpha) \times v_2$. If $v \geq 0$, we classify the picture to be a cat picture; otherwise, we classify the picture to be a dog picture. We use different $\alpha$ to form different classifiers and use them to test on our training examples. Then we find one with the highest correction rate, and use that classifier to classify test examples to calculate correction rate. \\
\begin{table}[h]
\caption{Combined Feature Training Result}
\centering
\begin{tabular}{| p{8cm}| l | l | l | l |}
\hline
Two feature vectors $F_1$ and $F_2$ & \multicolumn{4}{|c|}{Correction Rate} \\ \cline{2-5}
 & $F_1$ & $F_2$ & approach1 & approach2 \\
\hline
$F_1$ = RGB($n=1,x=10,y=10,z=10$), $F_2$ = TF1($n=16,N_f=24$) & 71.9\% & 66.5\% & 73.1\% & 73.8 \% \\
\hline
$F_1$ = HSV($n=3,x=10,y=10,z=10$), $F_2$ = TF1($n=8,N_f=24$) & 72.7\% & 67.1\% & 73.6\% & 74.5 \% \\
\hline
\end{tabular}
\end{table}\\
From Table 3, we can see that both of the approaches achieve a better correction rate, and approach 2 is better than approach 1.

>>>>

\section {Combination of Color and Texture Feature}
Assume that color feature vector has a length of $N_c$, the texture feature has a length of $N_t$. Our first approach is to concatenate the two feature vectors into a longer feature vector with a length of $N_c + N_t$. Then we will run boosting algorithm using the new feature vector. \\
The second approach is combining two classifiers instead of combing two feature vectors. Recall that for boosting classifier, each picture will have a voting. Assume that classfier 1 gives the picture a voting $v_1$, and classifier 2 gives the picture a voting $v_2$. Given parameter $\alpha$, we calculate a new voting $ v = \alpha \times v_1 + (1-\alpha) \times v_2$. We use different $\alpha$ to form different classifiers and use them to test on our training examples, and find one with the highest correction rate.
\begin{table}[h]
\caption{Combined Feature Training Result}
\centering
\begin{tabular}{| p{8cm}| l | l | l | l |}
\hline
Two feature vectors $F_1$ and $F_2$ & \multicolumn{4}{|c|}{Correction Rate} \\ \cline{2-5}
 & $F_1$ & $F_2$ & approach1 & approach2 \\
\hline
$F_1$ = RGB($n=1,x=10,y=10,z=10$), $F_2$ = TF1($n=16,N_f=24$) & 71.9\% & 66.5\% & 73.1\% & 73.8 \% \\
\hline
$F_1$ = HSV($n=3,x=10,y=10,z=10$), $F_2$ = TF1($n=8,N_f=24$) & 72.7\% & 67.1\% & 73.6\% & 74.5 \% \\
\hline
\end{tabular}
\end{table}\\
From Table 3, we can see that both of the approaches achieve a better correction rate, and approach 2 is better than approach 1.
